Manuscript_Github_Pchabaudi_pir

### 2022-07-25 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Save zscore information and tables

                       h = Heatmap(heatmap_data,
                                   name = paste0('z-score',
                                                 extra_title),
                                   col = c(cbPalette[6],
                                           'white', 
                                           cbPalette[7]),
                                   row_names_gp = gpar(fontsize = ifelse(
                                     nrow(heatmap_data) > 13, 
                                     12*(13/nrow(heatmap_data)), 
                                     12)
                                   ),
                                   column_names_gp = gpar(fontsize = 10),
                                   row_dend_width = unit(3, "cm"),
                                   right_annotation = if(tpm_mat){
                                     tpm_ha
                                   }else{
                                     NULL
                                   },
                                   left_annotation = 
                                     if(identical(list_element,
                                                  dplyr::first(zscore_list)) & is.character(annotation_clade)){
                                       clade_ha
                                     }else{
                                       NULL
                                     }, 
                                   #Only want the clade annotation when it is first heatmap
                                   width = unit(4.5, 'cm'),
                                   cluster_columns = FALSE,
                                   height = unit(7,'cm'),
                                   row_title = NULL,
                                   cluster_rows = FALSE,
                                   column_title = paste(title),
                                   heatmap_legend_param = list(
                                     at = c(3,2,1,0,-1,-2,-3),
                                     labels_gp = gpar(fontsize = 10),
                                     title_gp = gpar(fontsize = 10)
                                   ),
                                   ...
                       )
                       return(h)
                     })

@@

```{r phaseograms_whole_genome}
if(global_save_var){
  pdf(file = 'plots/phaseogram_allgenes_rMTorder.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = chab_z.list,
                      gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = TRUE)
  dev.off()
}

if(global_save_var){
  pdf(file = 'plots/phaseogram_allgenes_SBPorder.pdf',
      height = 5,
      width = 5)
draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
  dev.off()
}

@@

>>>>

                       h = Heatmap(heatmap_data,
                                   name = paste0('z-score',
                                                 extra_title),
                                   col = c(cbPalette[6],
                                           'white', 
                                           cbPalette[7]),
                                   row_names_gp = gpar(fontsize = ifelse(
                                     nrow(heatmap_data) > 13, 
                                     12*(13/nrow(heatmap_data)), 
                                     12)
                                   ),
                                   column_names_gp = gpar(fontsize = 10),
                                   row_dend_width = unit(3, "cm"),
                                   right_annotation = if(tpm_mat){
                                     tpm_ha
                                   }else{
                                     NULL
                                   },
                                   left_annotation = 
                                     if(identical(list_element,
                                                  dplyr::first(zscore_list)) & is.character(annotation_clade)){
                                       clade_ha
                                     }else{
                                       NULL
                                     }, 
                                   #Only want the clade annotation when it is first heatmap
                                   width = unit(4.5, 'cm'),
                                   cluster_columns = FALSE,
                                   height = unit(7,'cm'),
                                   row_title = NULL,
                                   cluster_rows = FALSE,
                                   column_title = paste(title),
                                   heatmap_legend_param = list(
                                     at = rev(c(3,2,1,0,-1,-2,-3)),
                                     labels_gp = gpar(fontsize = 10),
                                     title_gp = gpar(fontsize = 10)
                                   ),
                                   ...
                       )
                       return(h)
                     })

@@

```{r phaseograms_whole_genome}
if(global_save_var){
  pdf(file = 'plots/phaseogram_allgenes_rMTorder.pdf',
      height = 5,
      width = 7)
  draw_heatmap_zscore(zscore_list = chab_z.list,
                      gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = TRUE)
  dev.off()
}

if(global_save_var){
  pdf(file = 'plots/phaseogram_allgenes_SBPorder.pdf',
      height = 5,
      width = 7)
draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
  dev.off()
}

@@

```{r zscore_save}
chab_z.df <- inner_join(chab_z.list[[1]]$zscores, 
                        chab_z.list[[2]]$zscores, 
                        by = 'Geneid')
write.csv(chab_z.df,
          file = 'data/Pchabaudi_z.csv',
          row.names = FALSE)
write.table(x = phaseogram_time_order$rMT$zscore_order$Geneid,
            file = 'data/Pchabaudi_z_phaseOrder_rMT.list',
            row.names = FALSE, col.names = FALSE)
write.table(x = phaseogram_time_order$SBP$zscore_order$Geneid,
            file = 'data/Pchabaudi_z_phaseOrder_SBP.list',
            row.names = FALSE, col.names = FALSE)
```
